%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
\documentclass[10pt, a4paper]{resume}

\geometry{left=1cm, top=.5cm, right=1cm, bottom=.5cm, footskip=.5cm}

\fontdir[fonts/]

\colorlet{awesome}{awesome-concrete}

\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%-------------------------------------------------------------------------------
\name{Andruskiewitsch}{Igor}
\position{Software Developer}

\extrainfo{Córdoba, Argentina}
\mobile{(+54) 9 351 340 3359}
\email{i.andruskiewitsch23@gmail.com}
\github{rusito-23}
\linkedin{igor-andruskiewitsch}
\stackoverflow{8189455}{rusito23}


%-------------------------------------------------------------------------------
\begin{document}

\makecvheader[L]

\makecvfooter
{ }
{Andruskiewitsch Igor~~~·~~~Resume}
{\thepage}


%-------------------------------------------------------------------------------
%	SECTION
%-------------------------------------------------------------------------------
\cvsection{Education}

\begin{cventries}

    %---------------------------------------------------------
    \cventry
    {FaMAF - UNC (National University of Cordoba)}
    {Computer Science}
    {Córdoba, Argentina}
    {Mar. 2016 - Present}
    {
        \begin{cvitems}
        \item {Analista en Computación (equivalent to Computer Science Bachelor)}
            \subitem {
                \textbullet{ GPA: 8.4 (10 scale) }
                \textbullet{ Taken subjects: 17/18 }
                \textbullet{ Expected graduation date: July 2021 }
            }
        \item{Licenciatura en Ciencias de la Computación (equivalent to Computer Science Mst.)}
            \subitem {
                \textbullet{ GPA: 8.4 (10 scale) }
                \textbullet{ Taken subjects : 17/28 }
                \textbullet{ Expected graduation date: January 2023 }
            }
        \item{Taken Subjects Highlights: \\
                \textbullet{ Data Structures \& Algorithms }
                \textbullet{ Neural Networks }
                \textbullet{ Probability and Statistics }
                \textbullet{ Numerical Analysis }
                \textbullet{ Software Engineering }
            }
        \end{cvitems}
    }

    %---------------------------------------------------------
\end{cventries}



%-------------------------------------------------------------------------------
%	SKILLS
%-------------------------------------------------------------------------------
\cvsection{Skills}

\begin{cvskills}

    %---------------------------------------------------------
    \cvskill
    {Mobile Development} {
        \textbullet{ Swift }
        \textbullet{ Objective C }
        \textbullet{ UIKit }
        \textbullet{ Tensorflow Lite }
        \textbullet{ CoreML }
    }

    %---------------------------------------------------------
    \cvskill
    {Data Science}{
        \textbullet{ Python } 
        \textbullet{ OpenCV  }
        \textbullet{ PyTorch }
        \textbullet{ Keras }
        \textbullet{ Numpy }
        \textbullet{ Pandas }
        \textbullet{ Matplotlib }
    }

    %---------------------------------------------------------
    \cvskill
    {Database}{
        \textbullet{ MySQL } 
        \textbullet{ SQLite }
        \textbullet{ RealmDB }
        \textbullet{ Mongo }
    }

    %---------------------------------------------------------
    \cvskill
    {Tools \& General Knowledge}{
        \textbullet{ C/C++ } 
        \textbullet{ BASH }
        \textbullet{ Javascript }
        \textbullet{ git }
        \textbullet{ Jira }
        \textbullet{ XCode }
        \textbullet{ Jupyter Lab }
    }

    %---------------------------------------------------------
    \cvskill
    {Languages} {
        \textbullet{ (Mother tongue) : Spanish }
        \textbullet{ (Fluent) : English, French }
        \textbullet{ (Basic) : Italian }
    }

    %---------------------------------------------------------
\end{cvskills}



%-------------------------------------------------------------------------------
%	EXPERIENCE
%-------------------------------------------------------------------------------
\cvsection{Experience}

\begin{cventries}

    %---------------------------------------------------------
    \cventry
    {iOS Developer}
    {Taller Technologies - Venmo (PayPal)}
    {Remote - Contractor}
    {Sept. 2020 - Present}
    {
        \begin{cvitems}
        \item {Used Swift with MVVM and Coordinator patterns}
        \item {Improved business profiles visibility, discovery and marketing}
        \item {Worked on picture comparison automation using structural similarity in Python}
        \end{cvitems}
    }


    %---------------------------------------------------------
    \cventry
    {Software Developer}
    {IncluIT / SimTLIX}
    {Córdoba, Argentina}
    {Jun. 2019 - Sept. 2020}
    {
        \begin{cvitems}
        \item{Developed macOS Firewall using Apple’s Network Extension framework with Swift, Objective C and C++ - Pulse Secure (VPN client)}
        \item{Investigated real-time semantic segmentation, using Keras and Tensorflow Lite in Python and C++ - Avaya Workspace (telecommunications app)}
        \item{Worked on improvement and bugfixing for the macOS and iOS apps using Objective C - Avaya Workspace (telecommunications app)}
        \item{Developed new flows from scratch and refactored several modules using Swift - Jerárquicos (health insurance company)}
        \item{Refactored internal dependencies from static to dynamic frameworks with XCode - Telecom Personal (telecommunications company)}
        \item{Improved the auth library to allow user differentiations in Swift - Telecom Personal (telecommunications company)}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {iOS Developer}
    {Globant}
    {Córdoba, Argentina}
    {Feb. 2019 - Jun. 2019}
    {
        \begin{cvitems}
        \item{Improved code style and quality fixing linter errors - Royal Caribbean (cruise company)}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Full Stack Developer}
    {JCOR}
    {Córdoba, Argentina}
    {Jun. 2018 - Feb. 2019}
    {
        \begin{cvitems}
        \item{Developed car-pooling flows and refactored login and register modules using Swift, Java (BE) and MySQL database - Taaxii (transportation app)}
        \item{Improved regressions by writing automation tests using Selenium and Appium - Taaxii (transportation app)}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Freelance Web developer}
    {AVH Club AR (Alexander von Humboldt Foundation Alumni Association in Argentina)}
    {Córdoba, Argentina}
    {Jun. 2017 - Jun. 2018}
    {
        \begin{cvitems}
        \item {Developed and maintained the AVHCLUBAR website\newline
            \textbullet{ Used PHP, MySQL, HTML, and CSS }
            \textbullet{ Developed Admin page (News - Blog - Photos) }
            \textbullet{ Automated mail campaigns using MailChimp} }
        \end{cvitems}
    }

    %---------------------------------------------------------
\end{cventries}


%-------------------------------------------------------------------------------
%	SECTION EXTRACURRICULAR
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}

\begin{cventries}

    %---------------------------------------------------------
    \cventry
    {Volunteer}
    {PyData}
    {Córdoba, Argentina}
    {2018 and 2019 editions}
    {
        \begin{cvitems}
        \item {Helped the Committee on different organizational tasks}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Scholar}
    {Conference on Computer Science (JCC)}
    {Rosario, Argentina.}
    {Oct. 25-27, 2017}
    {
        \begin{cvitems}
        \item {Received a scholarship to participate in the Conference in Computer Science at the National University of Rosario, Rosario, Argentina}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Participant}
    {Argentinian Programming Contest (TAP)}
    {FaMAF, Córdoba, Argentina.}
    {2017}
    {
        \begin{cvitems}
        \item {Based on resolving a series of mathematical and algorithmic problems using programming skills}
        \end{cvitems}
    }

    %---------------------------------------------------------
\end{cventries}

%-------------------------------------------------------------------------------
\end{document}
